---
title: 'Yield Analysis: All Lm.Cluster Figures'
author: "Austin Richards"
date: "3/13/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##Data

###Load libraries & data
```{r}

#load libraries
library(tidyverse)
require(estimatr)
library(dplyr)
library(readr)
library(ggplot2)
library(broom)
library(purrr)
library(dotwhisker)
library(estimatr)
library(readr)
library(mice)
library(miceadds)
library(Amelia)
library(RColorBrewer)
library(coefplot)
library(wesanderson)
library(multiwayvcov)
library(cowplot)

#load data
fieldcrop <- read_csv(url("https://vitalsigns-website-downloads.s3.amazonaws.com/tables/household_field_season_fieldcrop.csv"))
hh_fieldcrop <- read_csv(url("https://vitalsigns-website-downloads.s3.amazonaws.com/tables/household_fieldcrop.csv"))
field_season <- read_csv(url("https://vitalsigns-website-downloads.s3.amazonaws.com/tables/household_field_season.csv"))
hh_indiv <- read_csv(url("https://vitalsigns-website-downloads.s3.amazonaws.com/tables/household_individual.csv"))

```

###Data wrangling
```{r}
#Filter fieldcrop, treat factors as factors and numeric as numeric
fieldcrop <- dplyr::filter(fieldcrop, country == 'RWA', ag4a_15 != "na")
fieldcrop$ag4a_08 <- as.numeric(fieldcrop$ag4a_08)
fieldcrop$ag4a_15 <- as.numeric(fieldcrop$ag4a_15)
fieldcrop$ag4a_15_unit <- as.factor(fieldcrop$ag4a_15_unit)
fieldcrop$crop_name <- as.factor(fieldcrop$crop_name)
fieldcrop$ag4a_15_unit[which(fieldcrop$ag4a_15_unit=="Liter")] <- "Kg" #because this is a misentry
fieldcrop <- filter(fieldcrop, ag4a_15_unit == "Kg")

#fix crop name mismatches
fieldcrop$crop_name[which(fieldcrop$crop_name=="Irish potatoes")] <- "Irish Potatoes"
fieldcrop$crop_name[which(fieldcrop$crop_name=="Blood fruit")] <- "Blood Fruit"  

#Filter field_season, treat factors as factors and numeric as numeric
field_season <- filter(field_season, country == 'RWA',  ag3a_03 == 'Cultivated' )
field_season$ag3a_39 <- as.factor(field_season$ag3a_39)
field_season$ag3a_39a <- as.factor(field_season$ag3a_39a)
field_season$ag3a_39a_other <- as.factor(field_season$ag3a_39a_other)
field_season$ag3a_40 <- as.numeric(field_season$ag3a_40)
field_season$ag3a_45 <- as.factor(field_season$ag3a_45)
field_season$ag3a_47 <- as.factor(field_season$ag3a_47)

#fix crop name mismatch
field_season$ag3a_07_1[which(field_season$ag3a_07_1=="Irish potatoes")] <- "Irish Potatoes"
field_season$ag3a_07_1[which(field_season$ag3a_07_1=="Blood fruit")] <- "Blood Fruit"

#Set landscape # as factor in household survey data
hh_fieldcrop$landscape_no <- as.factor(hh_fieldcrop$landscape_no)

#Join fieldcrop and field_season dataframes
joined_df <- inner_join(field_season, fieldcrop, by =c("id"= "parent_id", 'round', "landscape_no", "country", "field_no", "hh_refno", "season"))

#Add columns for yield
joined_df <- mutate(joined_df, kg_peracre = ag4a_15/ag4a_08)
joined_df <- mutate(joined_df, kg_perha = kg_peracre*(1/.404686))

#per acre planted 
joined_df$ag4a_02[which(joined_df$ag4a_02=="1/4")] <- .25
joined_df$ag4a_02[which(joined_df$ag4a_02=="1/2")] <- .5
joined_df$ag4a_02[which(joined_df$ag4a_02=="3/4")] <- .75
joined_df$ag4a_02[which(joined_df$ag4a_02=="Almost All")] <- 1
joined_df$ag3a_40 <- as.numeric(joined_df$ag3a_40)
joined_df$ag3a_47 <- as.numeric(joined_df$ag3a_47)
joined_df$ag4a_02 <- as.numeric(joined_df$ag4a_02)

joined_df <- mutate(joined_df, kg_peracre_planted = case_when(ag4a_01 == TRUE ~ kg_peracre, ag4a_01 == FALSE ~ ag4a_15/(ag4a_08*ag4a_02))) %>% 
  mutate(kg_perha_planted = kg_peracre_planted *(1/.404686))

#value per hectare planted 
joined_df <- filter(joined_df, kg_perha_planted != Inf) %>% 
  mutate(value_peracre = ag4a_16/ag4a_08) %>% 
  mutate(value_perha = value_peracre*(1/.404686)) %>% 
  mutate(value_peracre_planted = case_when(ag4a_01 == TRUE ~ value_peracre, ag4a_01 == FALSE ~ ag4a_16/ag4a_08*ag4a_02)) %>% 
  mutate(value_perha_planted = value_peracre_planted *(1/.404686))

#Add column for pesticide kg per hectare planted
joined_df <-mutate(joined_df, pesticide_use_kg = ifelse(ag3a_60_2 == "Millilitre", ag3a_60_1*0.001, ag3a_60_1)) %>% 
  mutate(pesticide_use_kg = case_when(ag3a_58 == TRUE ~ pesticide_use_kg, ag3a_58 == FALSE ~ 0)) %>% 
  mutate(pest_peracre = pesticide_use_kg/ag4a_08) %>% 
  mutate(pest_perha = pest_peracre*(1/.404686)) %>% 
  mutate(pest_peracre_planted = case_when(ag4a_01 == TRUE ~ pest_peracre, ag4a_01 == FALSE ~ pest_peracre/ag4a_02)) %>% 
  mutate(pest_perha_planted = pest_peracre_planted *(1/.404686))

#Add column for inorg fert kg per hectare planted
joined_df <- mutate(joined_df, inorg_peracre = ag3a_47/ag4a_08) %>% 
  mutate(inorg_perha = inorg_peracre*(1/.404686)) %>%  
  mutate(inorg_perha_planted = case_when(ag4a_01 == TRUE ~ inorg_perha, ag4a_01 == FALSE ~ inorg_perha/ag4a_02)) %>% 
  mutate(inorg_perha_planted = case_when(ag3a_45 ==TRUE ~ inorg_perha_planted, ag3a_45 == FALSE ~ 0 ))

#Add column for org fert kg per hectare planted
joined_df <- mutate(joined_df, org_peracre = ag3a_40/ag4a_08) %>% 
  mutate(org_perha = org_peracre*(1/.404686)) %>%
  mutate(org_perha_planted = case_when(ag4a_01 == TRUE ~ org_peracre, ag4a_01 == FALSE ~ org_perha/ag4a_02)) %>% 
  mutate(org_perha_planted = case_when(ag3a_39 ==TRUE ~ org_perha_planted, ag3a_39 == FALSE ~ 0 ))

```


```{r}
##Filter to only retain households in Rwanda, aggregate income categories by household

hh_indiv <- filter(hh_indiv, country == "RWA")

hh_nonag_income <- aggregate(hh_e65_1 ~ hh_refno, FUN = sum, data = hh_indiv )

hh_business_rev <- aggregate(hh_e64_1 ~ hh_refno, FUN = sum, data = hh_indiv) 

joined_df <- right_join(hh_nonag_income, joined_df, by = "hh_refno")

```


```{r}
#make cluster variable for unique field id
joined_df <- mutate(joined_df, cluster = paste(hh_refno, field_no, sep='-'))

#now df is filtered to only include 'main crops' from a field
df_maincr <- filter(joined_df, crop_name == ag3a_07_1)
df_maincr$crop_name[which(df_maincr$crop_name=="Blood fruit")] <- "Blood Fruit"

df <- df_maincr
```


```{r}
#trimmming top and bottom 2.5% of yield (kg) observations for every crop in df

cr <- unique(df$crop_name)
df <- df[!is.na(df$ag4a_04),] #Removes NA value for intercropping (this is removing just one single obs)

#create exclude variable

df$exclude_2.5 <- NA


for(i in 1:length(cr)){

df$exclude_2.5[df$crop_name==cr[i]] <- ifelse(df$kg_perha_planted[df$crop_name==cr[i]] > quantile(df$kg_perha_planted[df$crop_name==cr[i]], probs=0.975) | df$kg_perha_planted[df$crop_name==cr[i]] < quantile(df$kg_perha_planted[df$crop_name==cr[i]], probs=0.025), 1, 0)

}

table(df$exclude_2.5, useNA="always")

df <- df[df$exclude_2.5==0,]

```


```{r}
#scaling pesticdes and inorganic fertilizer to 10 kg units, and organic fertilizer to 100 kg unit

df$org_perha_planted <- df$org_perha_planted/100

df$inorg_perha_planted <- df$inorg_perha_planted/10

df$pest_perha_planted <- df$pest_perha_planted/10

# NOW "df" is master joined data frame, trimmed to only retain "main crops", and, for each crop, trimmed of top and bottom 2.5% of observations of kgs of yield per HA planted, and fertilizer is scaled to 100s of kgs for organic, and pesticide and inorganic fertilizers are scaled to 10s of kgs
```


```{r}
#Replace all NA values to FALSE - we are assuming that if, during data entry, folks selected used "NA", there was no erosion control techniques being applied

df[c("ag3a_14")][is.na(df[c("ag3a_14")])] <- FALSE

```


###Linear models for each crop

```{r}
#making data frame with only crops of at least 30 observations, our minimum standard for regression models

n30<- df %>% 
group_by(crop_name) %>% filter(n() >= 30) %>%  droplevels() %>% 
  select("kg_perha_planted", "crop_name", "ag4a_04", "ag3a_14", "ag4a_19", "ag4a_23", "hh_e65_1", "org_perha_planted", "inorg_perha_planted", "pest_perha_planted", "landscape_no", "round", "season", "cluster") 
  

```


```{r}
colnames(n30)[colnames(n30)=="ag4a_04"] <- "intercropped"
colnames(n30)[colnames(n30)=="ag3a_14"] <- "erosion_c"
colnames(n30)[colnames(n30)=="hh_e65_1"] <- "hh_earnings"
colnames(n30)[colnames(n30)=="ag4a_19"] <- "purchased_seed"

#View(n30)
```


```{r}

#For each intervetion, creating a list which only reatains crops which a) had a minimum of 30 total observation in the data set b) had at least 5 which recieved the intervention

sometimes_ic <- subset(n30, intercropped == TRUE) %>%  droplevels()
sometimes_ic <- sometimes_ic %>% group_by(crop_name) %>% filter(n() >=5) %>%  droplevels() 
sometimes_ic <- unique(sometimes_ic$crop_name)

sometimes_ogf <- subset(n30, org_perha_planted > 0)  %>%  droplevels()
sometimes_ogf <- sometimes_ogf %>% group_by(crop_name) %>% filter(n() >=5) %>%  droplevels() 
sometimes_ogf <- unique(sometimes_ogf$crop_name)


sometimes_inogf <- subset(n30, inorg_perha_planted > 0) %>%  droplevels()
sometimes_inogf <- sometimes_inogf %>% group_by(crop_name) %>% filter(n() >= 5) %>%  droplevels() 
sometimes_inogf <- unique(sometimes_inogf$crop_name)

sometimes_seed <- subset(n30, purchased_seed == TRUE ) %>%  droplevels()
sometimes_seed <- sometimes_seed %>% group_by(crop_name) %>% filter(n() >= 5) %>%  droplevels() 
sometimes_seed <- unique(sometimes_seed$crop_name)


sometimes_pest<- subset(n30, pest_perha_planted > 0 ) %>%  droplevels()
sometimes_pest <- sometimes_pest%>% group_by(crop_name) %>% filter(n() >= 5) %>%  droplevels() 
sometimes_pest <- unique(sometimes_pest$crop_name)

sometimes_erode<- subset(n30, erosion_c == TRUE ) %>%  droplevels()
sometimes_erode <- sometimes_erode%>% group_by(crop_name) %>% filter(n() >= 5) %>%  droplevels() 
sometimes_erode <- unique(sometimes_erode$crop_name)

```


```{r}
#Specifying factors

n30$round <- as.factor(n30$round)
n30$landscape_no <- as.factor(n30$landscape_no)
n30$season <- as.factor(n30$season)
n30$cluster <- as.factor(n30$cluster)
```



### Simple linear models

```{r}
#running a cluster regression for each crop which met criteria above, for each intervention. Recall data has already been trimmed of top and bottom 2.5% of yield observations for each crop.
#robust standard errors are clustered on unique plot id (which I've created and named "cluter" (that's just what lm.cluster is doing to acccount for the fact that yield may be partially dependend on unique plot id). Each regression controls for landscape, round and season)


inter_lm <- n30 %>% 
  group_by(crop_name) %>% 
  filter(crop_name %in% sometimes_ic) %>% 
    do(tidy(lm_robust(kg_perha_planted ~ intercropped + landscape_no + round + season, clusters = cluster,
             data = . )))

ogfert_lm <- n30 %>% 
  group_by(crop_name) %>% 
  filter(crop_name %in% sometimes_ogf ) %>% 
    do(tidy(lm_robust(kg_perha_planted ~ org_perha_planted + landscape_no + round + season, clusters = cluster,
             data = . )))

inogfert_lm <- n30 %>% 
  group_by(crop_name) %>% 
  filter(crop_name %in% sometimes_inogf ) %>% 
  filter(n() >= 5) %>%  droplevels() %>% 
  do(tidy(lm_robust(kg_perha_planted ~ inorg_perha_planted + landscape_no + round + season, clusters = cluster,
             data = . )))

seed_lm <- n30  %>% 
  group_by(crop_name) %>% 
  filter(crop_name %in% sometimes_seed ) %>%  
  filter(n() >= 5) %>%  droplevels() %>% 
   do(tidy(lm_robust(kg_perha_planted ~ purchased_seed + landscape_no + round + season, clusters = cluster,
             data = . )))

pest_lm <- n30 %>% 
  group_by(crop_name) %>% 
  filter(crop_name %in% sometimes_pest ) %>%  
  do(tidy(lm_robust(kg_perha_planted ~ pest_perha_planted + landscape_no + round + season, clusters = cluster,
             data = . )))

erode_lm <- n30 %>% 
  group_by(crop_name) %>% 
  filter(crop_name %in% sometimes_erode ) %>%  
  filter(crop_name != "Pyrethrum") %>%   #including pyrethrum does not allow us to do this regression
  do(tidy(lm_robust(kg_perha_planted ~ erosion_c + landscape_no + round + season, clusters = cluster,
             data = . )))

```



```{r}
###Creating a custom theme

theme_vsr <- function () { 
    theme_classic(base_size=9, base_family="Avenir")+
    theme(plot.title = element_text(face="bold"), legend.title = element_text(face="bold"))
}

```


###Simple linear model coefficient plots
(note we refer to simple linear model, when we really mean cluster linear model with only one explanatory variable)

```{r}

#Creating intercropping dataframe

inter_coefs <- filter(inter_lm, term =="intercroppedTRUE")
inter_coefs$term
inter_coefs$term[which(inter_coefs$term=="intercroppedTRUE")] <- "" #this gets rid of x axis lable on plot
inter_coefs$model <- inter_coefs$crop_name

inter_coefs$crop_name <- ordered(inter_coefs$crop_name, levels = c("Soyabeans", "Sorghum", "Maize", "Irish Potatoes", "Cassava", "Beans", "Banana Beer"))

str(inter_coefs$crop_name)

```



### Simple linear model: Organic fertilizer
```{r}
##Plotting organic fertilizer coefficients

ogfert_coefs <- filter(ogfert_lm, term =="org_perha_planted")
ogfert_coefs$term[which(ogfert_coefs$term=="org_perha_planted")] <- ""
ogfert_coefs$model <- ogfert_coefs$crop_name

lm_plot_org <- dwplot(ogfert_coefs, dodge_size =  .7)+
  geom_vline(xintercept = 0, linetype = 'dashed', colour = "darkgrey"  )+
  ggtitle("95% Confidence Interval: Organic Fertilizer")+
xlab("Crop yield (kg/hectare)")+
  scale_color_manual(name="Crop Type", values = c("#a6cd5b", "#eb8932", "#85bcc1", "#eb4024", "#e8af3c", "#55ad71", "#70519b", "#3f7a82", "#9c8dc3")) +
  theme_vsr()

lm_plot_org

# ggsave("lm_plot_org.png", plot = lm_plot_org, device = "png", path = "~/Documents/Bren/GP/3Graphs/Poster/",
#   width = 4, height = 3.3, units = c("in"),
#   dpi = 300)

```


### Simple linear model: Inorganic fertilizer
```{r}

##Plotting inorganic fertilizer coefficients

inogfert_coefs <- filter(inogfert_lm, term =="inorg_perha_planted")
inogfert_coefs$term[which(inogfert_coefs$term=="inorg_perha_planted")] <- "" 
inogfert_coefs$model <- inogfert_coefs$crop_name

lm_plot_inorg <- dwplot(inogfert_coefs, dodge_size =  .7)+
ggtitle("Inorg Fert Coefficients:\nKGs Per HA Planted")+
  geom_vline(xintercept = 0, linetype = 'dashed', colour = "darkgrey"  )+
  ggtitle("95% Confidence Interval: Inorganic Fertilizer")+
xlab("Crop yield (kg/hectare)")+
  scale_color_manual(name="Crop Type", values = c("#eb8932", "#eb4024", "#e8af3c", "#a66f5b","#3f7a82", "#9c8dc3")) +
  theme_vsr()

lm_plot_inorg

# ggsave("lm_plot_inorg.png", plot = lm_plot_inorg, device = "png", path = "~/Documents/Bren/GP/3Graphs/Poster/",
#   width = 4, height = 3.3, units = c("in"),
#   dpi = 300)

```


### Simple linear model: Pesticides
```{r}

##Plotting Pesticide ccoefficients

pest_coefs <- filter(pest_lm, term =="pest_perha_planted")
pest_coefs$term[which(pest_coefs$term=="pest_perha_planted")] <- "" 
pest_coefs$model <- pest_coefs$crop_name

lm_plot_pest <- dwplot(pest_coefs, dodge_size =  .7)+
ggtitle("Pesticide Coefficients:\nKGs Per HA Planted")+
  geom_vline(xintercept = 0, linetype = 'dashed', colour = "darkgrey"  )+
  ggtitle("95% Confidence Interval: Pesticides")+
xlab("Crop yield (kg/hectare)")+
  scale_color_manual(name="Crop Type", values = c("#eb8932", "#eb4024", "#e8af3c", "#a66f5b")) +
  theme_vsr()

lm_plot_pest

# ggsave("lm_plot_pest.png", plot = lm_plot_pest, device = "png", path = "~/Documents/Bren/GP/3Graphs/Poster/",
#   width = 4, height = 3.3, units = c("in"),
#   dpi = 300)

```


### Simple linear model: Intercropping
```{r}
##Plotting intercropping coefficients

lm_plot_inter <- 
dwplot(inter_coefs, dodge_size =  .7)+
  geom_vline(xintercept = 0, linetype = 'dashed', colour = "darkgrey"  )+
  ggtitle("95% Confidence Interval: Intercropping")+
  xlab("Crop yield (kg/hectare)")+
  scale_color_manual(name="Crop Type", values = c("#a6cd5b", "#eb8932", "#85bcc1", "#eb4024", "#e8af3c", "#55ad71", "#70519b")) +
  theme_vsr()

lm_plot_inter

# ggsave("lm_plot_inter.png", plot = lm_plot_inter, device = "png", path = "~/Documents/Bren/GP/3Graphs/Poster/",
#   width = 4, height = 3.3, units = c("in"),
#   dpi = 300)

```


### Simple linear model: Improved Seeds
```{r}
##Plotting improved seed coeffecients 

seed_coefs <- 
  filter(seed_lm, term =="purchased_seedTRUE")
seed_coefs$term[which(seed_coefs$term=="purchased_seedTRUE")] <- "" 
seed_coefs$model <- seed_coefs$crop_name

lm_plot_seed <- dwplot(seed_coefs, dodge_size =  .7)+
ggtitle("Improved Seed Coefficients:\nKGs Per HA Planted")+
  geom_vline(xintercept = 0, linetype = 'dashed', colour = "darkgrey"  )+
  ggtitle("95% Confidence Interval: Improved Seeds")+
  xlab("Crop yield (kg/hectare)")+
  scale_color_manual(name="Crop Type", values = c("#eb8932", "#85bcc1", "#eb4024", "#e8af3c", "#a66f5b", "#55ad71", "#70519b", "#3f7a82", "#9c8dc3")) +
  theme_vsr()

lm_plot_seed

# ggsave("lm_plot_seed.png", plot = lm_plot_seed, device = "png", path = "~/Documents/Bren/GP/3Graphs/Poster/",
#   width = 4, height = 3.3, units = c("in"),
#   dpi = 300)

```

### Simple linear model: Erosion Control
```{r}
##Plotting Erosion Control coefficients
erode_coefs <- 
  filter(erode_lm, term =="erosion_cTRUE")
erode_coefs$term[which(erode_coefs$term=="erosion_cTRUE")] <- "" 
erode_coefs$model <- erode_coefs$crop_name

lm_plot_erosion <- dwplot(erode_coefs, dodge_size =  .7)+
ggtitle("Erosion Control Coefficients:\nKGs Per HA Planted")+
  geom_vline(xintercept = 0, linetype = 'dashed', colour = "darkgrey"  )+
  ggtitle("95% Confidence Interval: Erosion Control")+
xlab("Crop yield (kg/hectare)")+
  scale_color_manual(name="Crop Type", values = c("#a6cd5b", "#eb8932", "#85bcc1", "#eb4024", "#e8af3c", "#a66f5b", "#55ad71", "#70519b", "#3f7a82", "#9c8dc3")) +
  theme_vsr()

lm_plot_erosion
#  relabel_predictors(c("erosion_cTRUE"=" "))+
#  theme(axis.ticks.y = element_blank())+

# ggsave("lm_plot_erosion.png", plot = lm_plot_erosion, device = "png", path = "~/Documents/Bren/GP/3Graphs/Poster/",
#   width = 4, height = 3.3, units = c("in"),
#   dpi = 300)

```


###Multiple regression coeficients
```{r}
#giving columns easier names 
colnames(df)[colnames(df)=="ag4a_04"] <- "intercropped"
colnames(df)[colnames(df)=="ag3a_14"] <- "erosion_c"
colnames(df)[colnames(df)=="ag4a_19"] <- "purchased_seed"
colnames(df)[colnames(df)=="hh_e65_1"] <- "hh_earnings"
```



```{r}

##Creating data frame for crops with greatest sample size

Beans <- filter(df, crop_name == "Beans" )

Potatoes <- filter(df,  crop_name == "Irish Potatoes" )

Maize <- filter(df, crop_name == "Maize" )

Paddy <- filter(df,  crop_name == "Paddy" )

Sorghum <- filter(df,  crop_name == "Sorghum" )

Soyabeans <- filter(df, crop_name == "Soyabeans" )

SP <- filter(df,  crop_name == "Sweet Potatoes" )

Wheat <- filter(df, crop_name == "Wheat" )

```



```{r}
##Creating data frame which only includes variables of interest for regression models for crops with greatest sample size

Beans <- select(Beans, "intercropped", "purchased_seed", "erosion_c", "inorg_perha_planted", "org_perha_planted", "pest_perha_planted", "landscape_no", "hh_earnings", "kg_perha_planted", "value_perha_planted", "round", "cluster", "season")

Potatoes <- select(Potatoes, "intercropped", "purchased_seed", "erosion_c", "inorg_perha_planted", "org_perha_planted", "pest_perha_planted","landscape_no", "hh_earnings", "kg_perha_planted", "value_perha_planted", "round","cluster", "season")

Maize <- select(Maize, "intercropped", "purchased_seed", "erosion_c", "inorg_perha_planted", "org_perha_planted","pest_perha_planted", "landscape_no", "hh_earnings", "kg_perha_planted", "value_perha_planted", "round", "cluster","season")

Paddy <- select(Paddy, "intercropped", "purchased_seed", "erosion_c", "inorg_perha_planted", "org_perha_planted","pest_perha_planted", "landscape_no", "hh_earnings", "kg_perha_planted", "value_perha_planted", "round","cluster", "season")

Sorghum <- select(Sorghum, "intercropped", "purchased_seed", "erosion_c", "inorg_perha_planted", "org_perha_planted", "pest_perha_planted", "landscape_no", "hh_earnings", "kg_perha_planted", "value_perha_planted", "round", "cluster", "season")

Soyabeans <- select(Soyabeans, "intercropped", "purchased_seed", "erosion_c", "inorg_perha_planted", "org_perha_planted","pest_perha_planted", "landscape_no", "hh_earnings", "kg_perha_planted", "value_perha_planted", "round", "cluster","season")

SP <- select(SP, "intercropped", "purchased_seed", "erosion_c", "inorg_perha_planted", "org_perha_planted","pest_perha_planted", "landscape_no", "hh_earnings", "kg_perha_planted", "value_perha_planted", "round","cluster", "season")

Wheat <- select(Wheat, "intercropped", "purchased_seed", "erosion_c", "inorg_perha_planted", "org_perha_planted", "pest_perha_planted","landscape_no", "hh_earnings", "kg_perha_planted", "value_perha_planted", "round","cluster", "season")

```



```{r}
###Running clustered regression models (standard errors clustered on variable "cluster", which is a unique plot ID, for crops with the greatest sample size, controlling for landscape round and season), and including all practices in each model and then plotting results in coeffecient plots


# df %>% 
#   group_by(crop_name) %>% 
#   tally()

#MLM PLOT BEANS
mod_boldc <-lm.cluster(kg_perha_planted ~  intercropped + erosion_c + purchased_seed +inorg_perha_planted + org_perha_planted + landscape_no, data = Beans, cluster = "cluster")

mlm_plot_beans <- coefplot(mod_boldc$lm_res, title = '\n\nBeans (n=647) ', ylab="", xlab = "Crop yield (kg/hectare)", color = "#eb8932", predictors = c("intercropped", "erosion_c", "purchased_seed", "inorg_perha_planted", "org_perha_planted", "pest_perha_planted"),  sort="alphabetical", newNames=c(erosion_cTRUE="Erosion Control", intercroppedTRUE = "Intercropped", purchased_seedTRUE = "Purchased Seed", inorg_perha_planted ="10s KGs of Inorganic Fertilizer", org_perha_planted = "100s KGs of Organic Fertilizer")) +
  theme_vsr()

mlm_plot_beans


#MLM PLOT IRISH POTATOES
mod_poldc <-lm.cluster(kg_perha_planted ~ intercropped + purchased_seed + inorg_perha_planted+ org_perha_planted + pest_perha_planted +  landscape_no + round + season + erosion_c, data = Potatoes, cluster = "cluster")

mlm_plot_irish_potatoes <- coefplot(mod_poldc$lm_res, title = '\n\nIrish Potatoes (n=191)', ylab="", xlab = "Crop yield (kg/hectare)", color="#eb4024", predictors = c("intercropped", "erosion_c", "purchased_seed", "inorg_perha_planted", "org_perha_planted","pest_perha_planted"),  sort="alphabetical", newNames=c(erosion_cTRUE="Erosion Control", intercroppedTRUE = "Intercropped", purchased_seedTRUE = "Purchased Seed", inorg_perha_planted ="10s KGs of Inorganic Fertilizer", org_perha_planted = "100s KGs of Organic Fertilizer", pest_perha_planted = "10s KGs of Pesticide"))+
  theme_vsr()

mlm_plot_irish_potatoes


#MLM PLOT MAIZE
mod_moldc <-lm.cluster(kg_perha_planted ~ intercropped + purchased_seed + inorg_perha_planted + org_perha_planted + pest_perha_planted +  landscape_no + round + season + erosion_c, data = Maize, cluster = "cluster")

mlm_plot_maize <- 
coefplot(mod_moldc$lm_res, predictors = c("intercropped", "erosion_c", "purchased_seed", "inorg_perha_planted", "org_perha_planted"), title = '\nMaize (n=348)', ylab="", xlab = "Crop yield (kg/hectare)", color = "#e8af3c",  sort="alphabetical", newNames=c(erosion_cTRUE="Erosion Control", intercroppedTRUE = "Intercropped", purchased_seedTRUE = "Purchased Seed", inorg_perha_planted ="10s KGs of Inorganic Fertilizer", org_perha_planted = "100s KGs of Organic Fertilizer"))+
  theme_vsr()

mlm_plot_maize


#MLM PLOT PADDY
mod_pyold <-lm.cluster(kg_perha_planted ~ intercropped + purchased_seed + inorg_perha_planted+ org_perha_planted + pest_perha_planted +  landscape_no + round + season + erosion_c, data = Paddy, cluster = "cluster")

mlm_plot_paddy <- 
coefplot(mod_pyold$lm_res, title = '\n\nPaddy (n= 35)', ylab="", xlab = "Crop yield (kg/hectare)", color="#a66f5b", predictors = c("intercropped", "erosion_c", "purchased_seed", "inorg_perha_planted", "org_perha_planted","pest_perha_planted"),  sort="alphabetical", newNames=c(erosion_cTRUE="Erosion Control", intercroppedTRUE = "Intercropped", purchased_seedTRUE = "Purchased Seed", inorg_perha_planted ="10s KGs of Inorganic Fertilizer", org_perha_planted = "100s KGs of Organic Fertilizer", pest_perha_planted = "10s KGs of Pesticide"))+
  theme_vsr()

mlm_plot_paddy


#MLM PLOT SORGHUM
mod_sold <-lm.cluster(kg_perha_planted ~ intercropped + purchased_seed + inorg_perha_planted+ org_perha_planted + pest_perha_planted +  landscape_no + round + season + erosion_c, data = Sorghum, cluster = "cluster")

mlm_plot_sorghum <- 
coefplot(mod_sold$lm_res, title = '\n\nSorghum (n= 78)', ylab="", xlab = "Crop yield (kg/hectare)", color="#55ad71", predictors = c("intercropped", "erosion_c", "purchased_seed", "inorg_perha_planted", "org_perha_planted","pest_perha_planted"),  sort="alphabetical", newNames=c(erosion_cTRUE="Erosion Control", intercroppedTRUE = "Intercropped", purchased_seedTRUE = "Purchased Seed", inorg_perha_planted ="10s KGs of Inorganic Fertilizer", org_perha_planted = "100s KGs of Organic Fertilizer", pest_perha_planted = "10s KGs of Pesticide"))+
  theme_vsr()

mlm_plot_sorghum


#MLM PLOT SOYABEANS
mod_soyold <-lm.cluster(kg_perha_planted ~ intercropped + purchased_seed + inorg_perha_planted+ org_perha_planted + pest_perha_planted +  landscape_no + round + season + erosion_c, data = Soyabeans, cluster = "cluster")

mlm_plot_soyabeans <- 
coefplot(mod_soyold$lm_res, title = '\n\nSoyabeans (n= 32)', ylab="", xlab = "Crop yield (kg/hectare)", color="#70519b", predictors = c("intercropped", "erosion_c", "purchased_seed", "inorg_perha_planted", "org_perha_planted","pest_perha_planted"),  sort="alphabetical", newNames=c(erosion_cTRUE="Erosion Control", intercroppedTRUE = "Intercropped", purchased_seedTRUE = "Purchased Seed", inorg_perha_planted ="10s KGs of Inorganic Fertilizer", org_perha_planted = "100s KGs of Organic Fertilizer", pest_perha_planted = "10s KGs of Pesticide"))+
  theme_vsr()

mlm_plot_soyabeans


#MLM PLOT SWEET POTATOES
mod_spoldc <-lm.cluster(kg_perha_planted ~ intercropped +  erosion_c + purchased_seed + inorg_perha_planted + org_perha_planted  + landscape_no, data = SP, cluster = "cluster")

mlm_plot_sweet_potatoes <- coefplot(mod_spoldc$lm_res, title = '\nSweet Potatoes (n= 87)', ylab="", xlab = "Crop yield (kg/hectare)", color = "#3f7a82", predictors = c("intercropped", "erosion_c", "purchased_seed", "inorg_perha_planted", "org_perha_planted"),  sort="alphabetical", newNames=c(erosion_cTRUE="Erosion Control", intercroppedTRUE = "Intercropped", purchased_seedTRUE = "Purchased Seed", inorg_perha_planted ="10s KGs of Inorganic Fertilizer", org_perha_planted = "100s KGs of Organic Fertilizer")) +
  theme_vsr()

mlm_plot_sweet_potatoes


#MLM PLOT WHEAT
mod_wold <-lm.cluster(kg_perha_planted ~ intercropped + purchased_seed + inorg_perha_planted+ org_perha_planted + pest_perha_planted +  landscape_no + round + season + erosion_c, data = Wheat, cluster = "cluster")
mlm_plot_wheat <- 
coefplot(mod_wold$lm_res, title = '\n\nWheat (n= 38)', ylab="", xlab = "Crop yield (kg/hectare)", color="#9c8dc3", predictors = c("intercropped", "erosion_c", "purchased_seed", "inorg_perha_planted", "org_perha_planted","pest_perha_planted"),  sort="alphabetical", newNames=c(erosion_cTRUE="Erosion Control", intercroppedTRUE = "Intercropped", purchased_seedTRUE = "Purchased Seed", inorg_perha_planted ="10s KGs of Inorganic Fertilizer", org_perha_planted = "100s KGs of Organic Fertilizer", pest_perha_planted = "10s KGs of Pesticide"))+
  theme_vsr()

mlm_plot_wheat

```



```{r}
#stylizing plots


mlm_first4 <- 
ggdraw() +
  draw_plot(mlm_plot_beans, x = 0, y = .5, width = .5, height = .5) +
  draw_plot(mlm_plot_irish_potatoes, x = .5, y = .5, width = .5, height = .5) +
  draw_plot(mlm_plot_maize, x = 0, y = 0, width = .5, height = 0.5) +
  draw_plot(mlm_plot_paddy, x = .5, y = 0, width = .5, height = 0.5) 
  draw_label("95% Confidence interval of Multiple Linear Regression Coefficients: Harvest Volume", x=.5, y=.97, fontfamily = "Avenir")

mlm_first4


mlm_last4 <- 
ggdraw() +
  draw_plot(mlm_plot_sorghum, x = 0, y = .5, width = .5, height = .5) +
  draw_plot(mlm_plot_soyabeans, x = .5, y = .5, width = .5, height = .5) +
  draw_plot(mlm_plot_sweet_potatoes, x = 0, y = 0, width = .5, height = 0.5) +
  draw_plot(mlm_plot_wheat, x = .5, y = 0, width = .5, height = 0.5) +
  draw_label("95% Confidence interval of Multiple Linear Regression Coefficients: Harvest Volume", x=.5, y=.97, fontfamily = "Avenir")

mlm_last4

#ALL MLM PLOTS
mlm_ALL <- 
ggdraw() +
  draw_plot(mlm_plot_beans, x = 0, y = .75, width = .5, height = .25) +
  draw_plot(mlm_plot_irish_potatoes, x = .5, y = .75, width = .5, height = .25) +
  draw_plot(mlm_plot_maize, x = 0, y = .5, width = .5, height = 0.25) +
  draw_plot(mlm_plot_paddy, x = .5, y = .5, width = .5, height = 0.25) +
  draw_plot(mlm_plot_sorghum, x = 0, y = .25, width = .5, height = .25) +
  draw_plot(mlm_plot_soyabeans, x = .5, y = .25, width = .5, height = .25) +
  draw_plot(mlm_plot_sweet_potatoes, x = 0, y = 0, width = .5, height = 0.25) +
  draw_plot(mlm_plot_wheat, x = .5, y = 0, width = .5, height = 0.25) +
  draw_label("95% Confidence interval of Multiple Linear Regression Coefficients: Harvest Volume", x=.5, y=.99, fontfamily = "Avenir")

mlm_ALL


# ggsave("mlm_ALL.png", plot = mlm_ALL, device = "png", path = "~/Documents/Bren/GP/3Graphs/Poster/",
#   width = 7.5, height = 8.5, units = c("in"),
#   dpi = 700)

```
