---
title: "IRC_tecate_survival"
author: "Rachel Kenny"
date: "9/2/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}

library(tidyverse)
library(here)
library(readxl)
library(janitor)

# Tecate data 
ph1 <- read_excel(here("data", "Phase1_data.xlsx")) %>% 
  clean_names()

ph2 <- read_excel(here("data", "Phase2_data.xlsx")) %>% 
  clean_names()

ph3 <- read_excel(here("data", "Phase3_data.xlsx")) %>% 
  clean_names()

# Soil data
soil1 <- read_excel(here("data", "Tecate_PhaseI_Topo1m_soil.xlsx")) %>% 
  clean_names()

soil2 <- read_excel(here("data", "Tecate_PhaseII_Topo1m_Soil.xlsx")) %>% 
  clean_names()

soil3 <- read_excel(here("data", "Tecate_PhaseIII_Topo1m_soil.xlsx")) %>% 
  clean_names()

# Climate data

clim1 <- read_excel(here("data", "PRISM_p1.xlsx")) %>% 
  clean_names()

clim2 <- read_excel(here("data", "PRISM_p2.xlsx")) %>% 
  clean_names()

clim3 <- read_excel(here("data", "PRISM_p3.xlsx")) %>% 
  clean_names()

```

## Data wrangling
```{r}

join1 <- inner_join(ph1, soil1, by = "id")

df1 <- join1 %>% 
  filter(july_2012_survival == 0 | july_2012_survival == 1) %>% 
  mutate(year_planted = "2011") %>% 
  select(id, site, year_planted, jan_2011hght_cm, july_2012_survival, aug_2012_shrub_cover, awc, clay, depth_t_rl, orgmat, ph, sand, slope1m, aspect1m, curvature)

colnames(df1) <- c("id","site", "year_planted", "height_planted", "survival_y1", "shrub_cover_y1", "awc", "clay", "depth_t_rl", "orgmat", "ph", "sand", "slope1m", "aspect1m", "curvature")

df1 <- inner_join(df1, clim1, by = "id")

# View(df1)

######################################

join2 <- inner_join(ph2, soil2, by = "id")

df2 <- join2 %>% 
  filter(july_13_survival == 0 | july_13_survival == 1) %>% 
  mutate(year_planted = "2012") %>% 
  select(id, site, year_planted, jan_12_height_cm, july_13_survival, july_12_percent_native_w_in_0_25m, awc, clay, depth_t_rl, orgmat, ph, sand, slope1m, aspect1m, curvature)

colnames(df2) <- c("id","site", "year_planted", "height_planted", "survival_y1", "shrub_cover_y1", "awc", "clay", "depth_t_rl", "orgmat", "ph", "sand", "slope1m", "aspect1m", "curvature")

df2 <- inner_join(df2, clim2, by = "id")

# View(join2)

######################################

join3 <- inner_join(ph3, soil3, by = "id") 

df3 <- join3 %>% 
  filter(x2016_survival == 0 | x2016_survival == 1) %>% 
  mutate(year_planted = "2015") %>% 
  select(id, site, year_planted, jan2015_hght_cm, x2016_survival, summer_2015_percent_shrub_cover, awc, clay, depth_t_rl, orgmat, ph, sand, slope1m, aspect1m, curvature)

colnames(df3) <- c("id","site", "year_planted", "height_planted", "survival_y1", "shrub_cover_y1", "awc", "clay", "depth_t_rl", "orgmat", "ph", "sand", "slope1m", "aspect1m", "curvature")

df3 <- inner_join(df3, clim3, by = "id")

# View(join3)

df_y1 <- rbind(df1, df2, df3)

df_y1$site <- as.factor(df_y1$site)
df_y1$year_planted <- as.factor(df_y1$year_planted)
df_y1$height_planted <- as.numeric(df_y1$height_planted)
df_y1$survival_y1 <- as.numeric(df_y1$survival_y1)
df_y1$shrub_cover_y1 <- as.numeric(df_y1$shrub_cover_y1)

```

## PH = ALL, Y = 1
## Binomial model
### Survival ~ site + year_planted + height_planted

```{r}

blm_y1 <- glm(survival_y1 ~ site + year_planted + height_planted, data = df_y1, family = "binomial")

summary(blm_y1)

```


## PH = ALL, Y = 2
## Binomial model
### Survival ~ site + year_planted + height_planted

```{r}

# View(join1)

df1 <- join1 %>% 
  filter(aug_2013_survival == 0 | aug_2013_survival == 1) %>% 
  mutate(year_planted = "2011") %>% 
  select(id, site, year_planted, jan_2011hght_cm, aug_2013_survival)

colnames(df1) <- c("id","site", "year_planted", "height_planted", "survival_y2")

# View(df1)

##

df2 <- join2 %>% 
  filter(july_14_survival == 0 | july_14_survival == 1) %>% 
  mutate(year_planted = "2012") %>% 
  select(id, site, year_planted, jan_12_height_cm, july_14_survival)

colnames(df2) <- c("id","site", "year_planted", "height_planted", "survival_y2")

# View(df2)

##

df3 <- join3 %>% 
  filter(x2017_survival == 0 | x2017_survival == 1) %>% 
  mutate(year_planted = "2015") %>% 
  select(id, site, year_planted, jan2015_hght_cm, x2017_survival)

colnames(df3) <- c("id","site", "year_planted", "height_planted", "survival_y2")

# View(df3)

df_y2 <- rbind(df1, df2, df3)

df_y2$site <- as.factor(df_y2$site)
df_y2$year_planted <- as.factor(df_y2$year_planted)
df_y2$height_planted <- as.numeric(df_y2$height_planted)
df_y2$survival_y2 <- as.numeric(df_y2$survival_y2)

```

## YEAR2 model results
```{r}

# View(df_y2)

blm_y2 <- glm(survival_y2 ~ site + year_planted + height_planted, data = df_y2, family = "binomial")

summary(blm_y2)

```


## PH = ALL, Y = 3
## Binomial model
### Survival ~ site + year_planted + height_planted
```{r}

# View(join1)

df1 <- join1 %>% 
  filter(july_2014_survival == 0 | july_2014_survival == 1) %>% 
  mutate(year_planted = "2011") %>% 
  select(id, site, year_planted, jan_2011hght_cm, july_2014_survival)

colnames(df1) <- c("id","site", "year_planted", "height_planted", "survival_y3")

# View(df1)

##

df2 <- join2 %>% 
  filter(july_15_survival == 0 | july_15_survival == 1) %>% 
  mutate(year_planted = "2012") %>% 
  select(id, site, year_planted, jan_12_height_cm, july_15_survival)

colnames(df2) <- c("id","site", "year_planted", "height_planted", "survival_y3")

# View(df2)

##

df3 <- join3 %>% 
  filter(x2018_survival == 0 | x2018_survival == 1) %>% 
  mutate(year_planted = "2015") %>% 
  select(id, site, year_planted, jan2015_hght_cm, x2018_survival)

colnames(df3) <- c("id","site", "year_planted", "height_planted", "survival_y3")

# View(df3)

df_y3 <- rbind(df1, df2, df3)

df_y3$site <- as.factor(df_y3$site)
df_y3$year_planted <- as.factor(df_y3$year_planted)
df_y3$height_planted <- as.numeric(df_y3$height_planted)
df_y3$survival_y3 <- as.numeric(df_y3$survival_y3)

```

## YEAR3 model
```{r}

# View(df_y3)

blm_y3 <- glm(survival_y3 ~ site + year_planted + height_planted, data = df_y3, family = "binomial")

summary(blm_y3)

```

## PH = 2 & #, Y = 1, SITE = 2
## Binomial model
### Survival ~ year_planted + height_planted
```{r}

df_y1_s2 <- df_y1 %>% 
  filter(site == 2) 

# View(df_y1_s2)

blm_y1_s2 <- glm(survival_y1 ~ year_planted + height_planted, data = df_y1_s2, family = "binomial")

summary(blm_y1_s2)

```


## PH = 2 & 3, Y = 1, SITE = 2
## Binomial model
### Survival ~ year_planted + height_planted + SOIL
```{r}

df_y1_s2 <- df_y1 %>% 
  filter(site == 2) 

View(df_y1_s2)

blm_y1_s2 <- glm(survival_y1 ~ year_planted + height_planted + shrub_cover_y1 + awc + clay + slope1m + aspect1m + curvature, data = df_y1_s2, family = "binomial")

blm_y1_s2 <- glm(survival_y1 ~ year_planted + awc + clay + slope1m, data = df_y1_s2, family = "binomial")

summary(blm_y1_s2)

```


## PH = 2 & 3, Y = 1, SITE = 2
## Binomial model
### Survival ~ year_planted + height_planted + SOIL + CLIM
```{r}

df_y1_s2 <- df_y1 %>% 
  filter(site == 2) 

hist(df_y1_s2$age1grow_sum_ppt) # 379.6 - 381
hist(df_y1_s2$age1grow_avg_tmin)
hist(df_y1_s2$age1grow_avg_tmean)
hist(df_y1_s2$age1grow_avg_tmax)
hist(df_y1_s2$age1non_g_sum_ppt) # 135.9 - 136.4
hist(df_y1_s2$age1non_g_avg_tmin)
hist(df_y1_s2$age1non_g_avg_tmean)
hist(df_y1_s2$age1non_g_avg_tmax)

summary(df_y1_s2)

View(df_y1_s2)

blm_y1_s2 <- glm(survival_y1 ~ year_planted + awc + clay + slope1m, data = df_y1_s2, family = "binomial")

summary(blm_y1_s2)

```










